Review Paper Draft

### 2020-08-17 lmm-genetic-review.tex
Section 2.3: better DAGs

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{comment}
\usepackage{float}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{url}
\allowdisplaybreaks
\usepackage{natbib}
%\usepackage{biblatex}
%\AtEveryCitekey{%
%  \clearfield{note}%
%}
\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\usetikzlibrary{arrows}
\providecommand{\pb}[1]{\textcolor{red}{#1}}
\providecommand{\anna}[1]{\textcolor{blue}{#1}}
\newcommand{\bbeta}[1][]{\boldsymbol{\beta}{#1}}
\newcommand{\bbetaT}{\widetilde{\boldsymbol{\beta}}}
\newcommand{\bbetaHat}[1][]{\widehat{\boldsymbol{\beta}{#1}}}
\newcommand{\bgamma}{\boldsymbol{\gamma}}
\newcommand{\beps}[1][]{\boldsymbol{\varepsilon}{#1}}
\newcommand{\bepsT}[1][]{\widetilde{\boldsymbol{\varepsilon}{#1}}}
\newcommand{\bX}[1][]{\textbf{X}#1}
\newcommand{\bXT}[1][]{\widetilde{\textbf{X}{#1}}}
\newcommand{\bZ}{\textbf{Z}}
\newcommand{\bZT}{\widetilde{\textbf{Z}}}
\newcommand{\by}{\textbf{y}}
\newcommand{\byT}{\widetilde{\textbf{y}}}
\newcommand{\bD}{\textbf{D}}
\newcommand{\bK}{\textbf{K}}
\newcommand{\bI}{\textbf{I}}
\newcommand{\bV}{\textbf{V}}
\newcommand{\bu}{\textbf{u}}
\newcommand{\bU}{\textbf{U}}
\newcommand{\bR}{\textbf{R}}
\newcommand{\bW}{\textbf{W}} 
\newcommand{\sigmaee}{\sigma^2_e}
\newcommand{\sigmagg}{\sigma^2_g}
\newcommand{\T}{\text{T}}

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{comment}
\usepackage{float}
\usepackage{color}
\usepackage{tikz}
\usepackage{tkz-euclide}

% Tikz settings optimized for causal graphs.
% Just copy-paste this part
\usetikzlibrary{shapes,decorations,decorations.markings,arrows,calc,arrows.meta,fit,positioning}
\tikzset{
    -Latex,auto,node distance =1 cm and 3 cm,semithick,
    state/.style ={ellipse, draw, minimum width = 0.7 cm},
    point/.style = {circle, draw, inner sep=0.04cm,fill,node contents={}},
    bidirected/.style={Latex-Latex,dashed},
    el/.style = {inner sep=2pt, align=left, sloped},
    strike through/.append style={
    decoration={markings, mark=at position 0.5 with {
    \draw[-] ++ (-4pt,-4pt) -- (4pt,4pt);}
  },postaction={decorate}}
}

\usepackage{subcaption}
\usepackage{url}
\allowdisplaybreaks
\usepackage{natbib}
%\usepackage{biblatex}
%\AtEveryCitekey{%
%  \clearfield{note}%
%}
\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\usetikzlibrary{arrows}
\providecommand{\pb}[1]{\textcolor{red}{#1}}
\providecommand{\anna}[1]{\textcolor{blue}{#1}}
\newcommand{\bbeta}[1][]{\boldsymbol{\beta}{#1}}
\newcommand{\bbetaT}{\widetilde{\boldsymbol{\beta}}}
\newcommand{\bbetaHat}[1][]{\widehat{\boldsymbol{\beta}{#1}}}
\newcommand{\bgamma}{\boldsymbol{\gamma}}
\newcommand{\beps}[1][]{\boldsymbol{\varepsilon}{#1}}
\newcommand{\bepsT}[1][]{\widetilde{\boldsymbol{\varepsilon}{#1}}}
\newcommand{\bX}[1][]{\textbf{X}#1}
\newcommand{\bXT}[1][]{\widetilde{\textbf{X}{#1}}}
\newcommand{\bZ}{\textbf{Z}}
\newcommand{\bZT}{\widetilde{\textbf{Z}}}
\newcommand{\by}{\textbf{y}}
\newcommand{\byT}{\widetilde{\textbf{y}}}
\newcommand{\bD}{\textbf{D}}
\newcommand{\bK}{\textbf{K}}
\newcommand{\bI}{\textbf{I}}
\newcommand{\bV}{\textbf{V}}
\newcommand{\bu}{\textbf{u}}
\newcommand{\bU}{\textbf{U}}
\newcommand{\bR}{\textbf{R}}
\newcommand{\bW}{\textbf{W}} 
\newcommand{\sigmaee}{\sigma^2_e}
\newcommand{\sigmagg}{\sigma^2_g}
\newcommand{\T}{\text{T}}

### 2020-08-17 main.tex
Section 2.3: better DAGs

\begin{figure}[H]
\centering
\begin{tikzpicture}[%
>=latex',
circ/.style={draw, shape=circle, node distance=1cm, line width=1pt}]%Define the arrow type and style for circled nodes
\draw[dashed] (0,1) node[left] (P) {Population Stratification} -- (2,1) node[right] (E) {Environment}; 
\draw[->] (0,0) node[left] (X) {Observed SNPs} -- (2,0) node[right] (Y) {Phenotype}; %Line between X and Y
\draw[->] (P)   -- (X) ; 
\draw[->] (E)   -- (Y) ; 
% \filldraw[color=red!60, fill=none, very thick] (0,1) ellipse (4.5 and 0.35);
\end{tikzpicture}
\caption{Directed acyclic graph (DAG) of confounding due to population structure.}
\label{fig:ps_env}
\end{figure}

@@

\anna{make better slashed arrows / DAGs}

\begin{figure}[H]
\centering
\begin{tikzpicture}[%
>=latex',
circ/.style={draw, shape=circle, node distance=1cm, line width=1pt}]%Define the arrow type and style for circled nodes
\draw[dashed] (0,1) node[left] (P) {Population Stratification} -- (2,1) node[right] (E) {Environment};
\draw[->] (0,0) node[left] (X) {Observed SNPs} -- (2,0) node[right] (Y) {Phenotype}; %Line between X and Y
\draw[->, red] (P) --node {|} (X) ; 
\draw[->] (E)   -- (Y) ; 
% \filldraw[color=red!60, fill=none, very thick] (0,1) ellipse (4.5 and 0.35);
\end{tikzpicture}
\caption{The causal pathway between the environment and observed SNPs may be indirectly blocked by many methods that attempt to reduce confounding due to population structure.}
\label{fig:ps_env_block}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}[%
>=latex',
circ/.style={draw, shape=circle, node distance=1cm, line width=1pt}]%Define the arrow type and style for circled nodes
\draw[dashed, red] (0,1) node[left] (P) {Population Stratification} --node {X} (2,1) node[right] (E) {Environment};
\draw[->] (0,0) node[left] (X) {Observed SNPs} -- (2,0) node[right] (Y) {Phenotype}; %Line between X and Y
\draw[->] (P) -- (X) ; 
\draw[->] (E)   -- (Y) ; 
% \filldraw[color=red!60, fill=none, very thick] (0,1) ellipse (4.5 and 0.35);
\end{tikzpicture}
\caption{The causal pathway between the environment and observed SNPs may be blocked if genetic information does not serve as an accurate proxy for it.}
\label{fig:ps_env_block2}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \node (1) at (0,0) {Population Stratification};
    \node (2) [right = of 1] {Environment};
    \node (3) [below = of 1] {Observbed SNPs};
    \node (4) [below = of 2] {Phenotype};
    \path[bidirected, -] (1) edge (2);
    \path (1) edge (3);
    \path (2) edge (4);
    \path (3) edge (4);
\end{tikzpicture}
\caption{Directed acyclic graph (DAG) of confounding due to population structure.}
\label{fig:ps_env}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \node (1) at (0,0) {Population Stratification};
    \node (2) [right = of 1] {Environment};
    \node (3) [below = of 1] {Observbed SNPs};
    \node (4) [below = of 2] {Phenotype};
    \path[bidirected, -] (1) edge (2);
    \path[red, line width = 0.5] (1) edge (3);
    \path (2) edge (4);
    \path (3) edge (4);
    \tkzMarkSegment[color=red,pos=.5,mark=x](1,3)
\end{tikzpicture}
\caption{The causal pathway between the environment and observed SNPs may be indirectly blocked by many methods that attempt to reduce confounding due to population structure.}
\label{fig:ps_env_block}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \node (1) at (0,0) {Population Stratification};
    \node (2) [right = of 1] {Environment};
    \node (3) [below = of 1] {Observbed SNPs};
    \node (4) [below = of 2] {Phenotype};
    \path[bidirected, -, red] (1) edge (2);
    \path (1) edge (3);
    \path (2) edge (4);
    \path (3) edge (4);
    \tkzMarkSegment[color=red,pos=.5,mark=x](1,2)
\end{tikzpicture}
\caption{The causal pathway between the environment and observed SNPs may be blocked if genetic information does not serve as an accurate proxy for it.}
\label{fig:ps_env_block2}
\end{figure}
